Challenging Fuel Cycle Modeling Assumptions: Facility and Time Step Discretization Effects

### 2016-02-08 paper.tex
explain recipe sources better. update references

Because the standard package of archetypes included with Cyclus does not
include a fleet-based reactor model, one was necessarily developed. A
simulation scenario was created that is roughly based on prior and ongoing
work in the Department of Energy (DOE) fuel cycle options campaign.  A few
phenomena related to the different modeling choices in each of the four cases
are identified and used as a basis for comparison.  These are
described in more detail in the following sections.

@@

The scenario starts with 100 LWRs and follows an exponential curve with a 1\%
annual growth rate for 200 years.  The decommissioning of the initial 100
reactors is staggered over years 15 to 55.  Fresh fuel for LWRs is provided directly from enrichment with infinite supply and throughput. In year 35, fast reactors become available for
deployment and no more thermal reactors are built.  LWR spent fuel separations
begins in year 15 with 2,000 MTHM/yr capacity and increases to 3,000 MTHM/yr in
year 25.  Fast reactor spent fuel separations and fuel fabrication have
infinite capacity.  All spent fuel is stored/cooled for 7 years before it becomes
available for separation: 5 years for cooling and an additional 2 years to approximate non-instantaneous separations and fabrication times. Figure \ref{fig:flow} shows the material flow
relationships between the facilities.  Compositions used for the simulations
were simple containing $^{238}U$, $^{235}U$, $^{239}Pu$, $^{241}Am$,
and small quantities of a few lanthanides.  Full composition details can be
found in the Cyclus input files used \cite{Carlsen2015}.

>>>>

Because the standard package of archetypes included with Cyclus does not
include a fleet-based reactor model, one was necessarily developed. A
simulation scenario was created that is roughly based on prior and ongoing
work in the Department of Energy (DOE) fuel cycle options campaign \cite{hoffman-eg23-2016}.  A few
phenomena related to the different modeling choices in each of the four cases
are identified and used as a basis for comparison.  These are
described in more detail in the following sections.

@@

The scenario starts with 100 LWRs and follows an exponential curve with a 1\%
annual growth rate for 200 years.  The decommissioning of the initial 100
reactors is staggered over years 15 to 55.  Fresh fuel for LWRs is provided directly from enrichment with infinite supply and throughput. In year 35, fast reactors become available for
deployment and no more thermal reactors are built.  LWR spent fuel separations
begins in year 15 with 2,000 MTHM/yr capacity and increases to 3,000 MTHM/yr in
year 25.  Fast reactor spent fuel separations and fuel fabrication have
infinite capacity.  All spent fuel is stored/cooled for 7 years before it becomes
available for separation: 5 years for cooling and an additional 2 years to approximate non-instantaneous separations and fabrication times. Figure \ref{fig:flow} shows the material flow
relationships between the facilities.

In fuel cycle simulation, it is common to use simplified fresh and discharged
fuel compositions that are consistent with results from externally performed
loading and burnup calculations. Compositions used in this analysis follow
this approach and are fixed (i.e. not dynamically computed in-situ).  These
compositions are the same as those used in similar transition analyses by
Hoffman, et al. \cite{hoffman-eg23-2016} and Littell, et al.
\cite{littell-cyclus-2015} containing $^{238}U$, $^{235}U$, $^{239}Pu$,
$^{241}Am$, and small quantities of a few other isotopes as place-holders
representing fission products. Exact composition details can be found in the
Cyclus input files used \cite{Carlsen2015}.
